** INSERT TITLE **

### 2016-03-03 papers/msystems_2016/Schloss_Commentary_mSystems_2016.Rmd

* Add new Swarm reference

The ability to assign 16S rRNA gene sequences to operational taxonomic units (OTUs) allows microbial ecologists to overcome the inconsistencies and biases within bacterial taxonomy and provides a strategy for clustering similar sequences that do not have representatives in a reference database. These sequences are clustered into OTUs based on their distance from (or similarity to) each other. Numerous algorithms for solving this seemingly simple problem have blossomed in recent years and were recently the subject of benchmarking studies performed by Westcott and myself [ref x 2], He et al. [ref], and Kopylova et al [ref]. These studies provide a thorough review of the sequencing clustering landscape, which can be divided into three general approaches: (i) *de novo* clustering where sequences are clustered without first mapping sequences to a reference database, (ii) closed-reference clustering where sequences are clustered based on the references that the sequences map to, and (iii) open reference clustering where sequences that do not map adequately to the reference are then clustered using a *de novo* approach. My studies have highlighted a persistent problem in the development of clustering algorithms, which is assessing the quality of the clustering assignments.

The most recent analysis of Kopylova et al [@ref] repeats many of the benchmarking strategies employed by previous researchers. First, they and others have compared the time and memory required to cluster sequences in a dataset [@Sun2009; @Cai2011; @Rideout2014; @Mah2014]. These are valid parameters to assess when judging a clustering method, but have little to say about the quality of the OTU assignments. In the extreme, we could easily develop a toy a clustering algorithm could randomly assign sequences to a predetermined number of OTUs and be efficient, but also poorly reflect the genetic diversity within the community. Second, they and others have compared the number of OTUs generated by various methods for a common dataset [@refs]. Again, the toy clustering algorithm could cluster to a target number of OTUs, but the clusterings would likely be meaningless. Third, because many of the methods are sensitive to the initial order of the sequences, a metric of OTU stability has been proposed as a way to assess algorithms [@He2015]. Although it is important that the methods generate reproducible OTU assignments, this approach ignores the possability that the variation in assignments may be equally robust or that the assignemnts by a highly reproducible algorithm may be quite poor. Fourth, the method that Kopylova et al. [@ref] relied upon the most was to cluster sequences from simulated data or data from synthetic communities of cultured organisms and quantify how well the OTU assignments matched the organisms' taxonomy [@Edgar2013; @Mah2014; @Barriuso2011; @Bonder2012; @Chen2013; @Huse2010; @May2014; @Cai2011; @Sun2011; @White2010]. This approach is flawed because bacterial taxonomy often reflects those inconsistencies and biases within bacterial taxonomy that OTU-based methods strive to overcome. Furthermore, this benchmarking strategy can only be applied when the actual taxonomy of the organisms are known and so it is unclear how the methods scale to sequences from the novel organisms we are likely to encounter in deep sequencing surveys. In a final approach, Kopylova and others have assessed the quality of clustering based on their ability to generate the same OTUs generated by other methods [@Schmidt2014Limits; @Rideout2014]. Unfortunately, without the ability to ground truth any method, such comparisons are tenuous. Westcott and I have proposed an unbiased and objective method for assessing the quality of OTU assignments that can be applied to any collection of sequences [@Schloss2011Assessing; @Westcott2015].

@@

To revisit these results, I have expanded the analysis to incorporate additional *de novo* and closed-reference algorithms and two simulated datasets following the approach described by Kopylova et al [@Kopylova2016]. I evaluated three heirarchical and seven greedy *de novo* algorithms, one open-reference clustering algorithm, and two closed-reference algorithms (Figure 1). To test these approaches I applied each of them to four datasets from soil [@Roesch2007], mouse feces [@Schloss2012Stabilization], and two simulated communities. The simulated communities were generated by randomly selecting 10,000 16S rRNA sequences that were unique within the V4 region from the SILVA non-redundant database [@ref]. Next, an even community was generated by specifying that each sequence had a frequency of 100 reads and a staggered community was generated by specifying that the abundance of each sequence was a randomly drawn a uniform distribution between 1 and 200. The benchmarking approach is the same as the approach used previously [@Westcott2015]. A reproducible version of this manuscript and analysis has been added to the repository available at https://github.com/SchlossLab/Schloss_Cluster_PeerJ_2015.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

The ability to assign 16S rRNA gene sequences to operational taxonomic units (OTUs) allows microbial ecologists to overcome the inconsistencies and biases within bacterial taxonomy and provides a strategy for clustering similar sequences that do not have representatives in a reference database. These sequences are clustered into OTUs based on their distance from (or similarity to) each other. Numerous algorithms for solving this seemingly simple problem have blossomed in recent years and were recently the subject of benchmarking studies performed by Westcott and myself [-@Schloss2011Assessing; -@Westcott2015], He et al. [-@He2015], and Kopylova et al [-@Kopylova2016]. These studies provide a thorough review of the sequencing clustering landscape, which can be divided into three general approaches: (i) *de novo* clustering where sequences are clustered without first mapping sequences to a reference database, (ii) closed-reference clustering where sequences are clustered based on the references that the sequences map to, and (iii) open reference clustering where sequences that do not map adequately to the reference are then clustered using a *de novo* approach. My studies have highlighted a persistent problem in the development of clustering algorithms, which is assessing the quality of the clustering assignments.

The most recent analysis of Kopylova et al [-@Kopylova2016] repeats many of the benchmarking strategies employed by previous researchers. First, they and others have compared the time and memory required to cluster sequences in a dataset [@Sun2009; @Cai2011; @Rideout2014; @Mah2014]. These are valid parameters to assess when judging a clustering method, but have little to say about the quality of the OTU assignments. In the extreme, we could easily develop a "toy" a clustering algorithm could randomly assign sequences to a predetermined number of OTUs and be efficient, but also poorly reflect the genetic diversity within the community. Second, they and others have compared the number of OTUs generated by various methods for a common dataset [@Edgar2013; @Kopylova2016]. Again, a toy clustering algorithm could cluster to a target number of OTUs, but the clusterings would likely be meaningless. Third, because many of the methods are sensitive to the initial order of the sequences, a metric of OTU stability has been proposed as a way to assess algorithms [@He2015]. Although it is important that the methods generate reproducible OTU assignments, this approach ignores the possability that the variation in assignments may be equally robust or that the assignemnts by a highly reproducible algorithm may be quite poor. Fourth, the method that Kopylova et al. [-@Kopylova2016] relied upon the most was to cluster sequences from simulated data or data from synthetic communities of cultured organisms and quantify how well the OTU assignments matched the organisms' taxonomy [@Edgar2013; @Mah2014; @Mah2015; @Barriuso2011; @Bonder2012; @Chen2013; @Huse2010; @May2014; @Cai2011; @Sun2011; @White2010; @AlGhalith2016]. This commonly used approach is flawed because bacterial taxonomy often reflects those inconsistencies and biases within bacterial taxonomy that OTU-based methods strive to overcome. Furthermore, this benchmarking strategy can only be applied when the actual taxonomy of the organisms are known and so it is unclear how the methods scale to sequences from the novel organisms we are likely to encounter in deep sequencing surveys. In a final approach, Kopylova and others have assessed the quality of clustering based on their ability to generate the same OTUs generated by other methods [@Schmidt2014Limits; @Rideout2014]. Unfortunately, without the ability to ground truth any method, such comparisons are tenuous. Westcott and I have proposed an unbiased and objective method for assessing the quality of OTU assignments that can be applied to any collection of sequences [@Schloss2011Assessing; @Westcott2015].

@@

To revisit these results, I have expanded the analysis to incorporate additional *de novo* and closed-reference algorithms and two simulated datasets following the approach described by Kopylova et al [@Kopylova2016]. I evaluated three heirarchical and seven greedy *de novo* algorithms, one open-reference clustering algorithm, and four closed-reference algorithms (Figure 1). To test these approaches I applied each of them to four datasets from soil [@Roesch2007], mouse feces [@Schloss2012Stabilization], and two simulated communities. The simulated communities were generated by randomly selecting 10,000 16S rRNA sequences that were unique within the V4 region from the SILVA non-redundant database [@Kopylova2016; @Pruesse2007]. Next, an even community was generated by specifying that each sequence had a frequency of 100 reads and a staggered community was generated by specifying that the abundance of each sequence was a randomly drawn a uniform distribution between 1 and 200. The benchmarking approach is the same as the approach used previously [@Westcott2015]. A reproducible version of this manuscript and analysis has been added to the repository available at https://github.com/SchlossLab/Schloss_Cluster_PeerJ_2015.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur.  Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.  Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.  Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
